\vspace{\baselineskip} The population of long-period transiting exoplanets \vspace{-2.5\baselineskip}

### 2016-07-22 document/ms.tex
Adding paragraph about #18

@@

>>>>

In \dfmfig{obs-dist}, we compare the \emph{observed} period and radius
distributions of our discoveries to the longest-period planet candidates
discovered transiting stars in our target list by the official \kepler\
transit search \citep{Coughlin:2016}.
These histograms do not take uncertainties or detection efficiency into
account so any conclusions based on these plots should be taken with caution.
That being said, the apparent deficit of planets in the period range between
600 and 1000~days cannot be explained by selection effects~--~in fact, the
geometric transit probability exacerbates the signal~--~and should be
investigated more thoroughly.
We postulate three scenarios and expect that the observed effect is the result
of some combination of the three:
\begin{itemize}
{\item the periods of some candidates are overestimated and the missing second
transit occurs in a data gap,}
{\item overestimated stellar densities leading to an overestimate of the
orbital periods and an underestimate of the radii, or}
{\item a physical rise in the frequency of giant planets at long orbital
periods.}
\end{itemize}
The first two scenarios could be confirmed or ruled out by detailed analysis
of each candidate system and follow-up data.
Any result would be physically interesting but a rigorous analysis that is
beyond the scope of this \paper\ would be required to make a conclusive claim.

@@

\begin{figure*}~\\
\begin{center}
\includegraphics[width=\textwidth]{figures/obs_dist.pdf}
\end{center}
\caption{%
A comparison between the observed orbital period and planet radius
distributions of the long-period planet candidates reported here (blue hatched
histogram) and the previously known planet candidates \citep{Coughlin:2016}
with periods longer than 200~days and radii in the range $1-10\,R_\oplus$
(orange histogram).
\dfmfiglabel{obs-dist}}~\\
\end{figure*}
